---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# malawiShapefiles

<!-- badges: start -->
<!-- badges: end -->

The goal of malawiShapefiles is to be the repository of Malawi administrative and water body shapefiles 

## Installation

You can install the released version of malawiShapefiles from [CRAN](https://CRAN.R-project.org) with:

``` r
#install.packages("malawiShapefiles")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mcewenkhundi/malawiShapefiles")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(malawiShapefiles)
library(sf)
library(tidyverse)
library(ggspatial)


ggplot() +
  geom_sf(data=malawi, aes(fill = bt_label)) +
  scale_fill_manual(values = alpha(c("#DDDDDD", "#FF851B")),guide=FALSE) +
  labs(y = "Latitude", 
       x = "Longitude",
       title = "Map of administrative districts of Malawi",
       subtitle = "Blantyre is marked orange") +
  geom_sf(data=malawi_lakes[malawi_lakes$NAME=="LAKE NYASA",], fill = "light blue", color = "blue") +
  theme_light() +
  annotation_scale(location = "bl", width_hint = 0.5) +
  annotation_north_arrow(location = "tr", style = north_arrow_fancy_orienteering)

```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
